Enabling conditions for effective community-based marine reserves in small-scale fisheries

### 2018-04-10 docs/paper/Villasenor-Derbez.Rmd
Updated manuscript with new model and included CI for socioeco graphs

@@

```{r load_data}
invert <- read.csv(file = here::here("data", "invertebrates.csv"))

fish <- read.csv(file = here::here("data", "fish.csv"))

conapesca <- read.csv(file = here::here("data", "conapesca.csv"))

@@

# Fish

## Biomass
B_IN <- fish %>% 
  biomass(com = "Isla Natividad") %>% 
  model(sfe = F)

@@

@@

# Invert plots
## Lobsters
L_plot <- plot_model(model = list(L_IN, L_ME, L_PH),
                     various = T,
                     model_names = c("IS", "ME", "PH"))  +
  theme(legend.justification = c(0, 0),
        legend.position = c(0, 0.4),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.direction = "horizontal") +
  scale_colour_brewer(guide = guide_legend(title.position = "top", nrow = 3), palette = "Set1")

## Abundance
I_N <- plot_model(model = list(Ni_IN, Ni_ME, Ni_PH),
                  various = T,
                  model_names = c("IN", "ME", "PH"))

# Fish plots
## Biomass
F_B <- plot_model(model = list(B_IN, B_ME, B_PH),
                 various = T,
                 model_names = c("IS", "ME", "PH"))

## Abundance
F_N <- plot_model(model = list(N_IN, N_ME, N_PH),
                  various = T,
                  model_names = c("IN", "ME", "PH"), legend = F)

@@

```{r, fig.height = 3, fig.width = 6, fig.cap = "\\label{fig:res_com}Summarized effects of the marne reserves by direction (positive - negative) and significance."}
observe <- function(model){
  tidy_terms <- model %>% 
        robust_se() %>%
        filter(grepl(":zonaReserva", term)) %$%
        str_split(term, pattern = ":", simplify = T) %>% 
        as.tibble() %>% 
        set_colnames(c("Ano", "Zona")) %>% 
        select(-Zona) %>% 
        mutate(Ano = as.numeric(gsub(Ano, pattern = "year", replacement = "")))

      p_i <- robust_se(model) %>%
        filter(grepl(":zonaReserva", term)) %>%
        cbind(tidy_terms) %>%
        mutate(ptest = ((p.value < 0.05)*-1)+0.05)

       return(p_i)
      }

IN <- list(N_IN, Ni_IN, B_IN, L_IN) %>%
  map_df(.f = observe) %>%
  as.tibble() %>% 
  select(estimate, p.value) %>% 
  mutate(Com = "Isla Natividad",
         n_ind = nrow(.))

@@

rbind(IN, ME, PH) %>% 
  mutate(direction = case_when(estimate < 0 ~ "Negative",
                               estimate > 0 ~ "Positive"),
         Significance = case_when(p.value < 0.05 ~ "p < 0.05",
                            p.value >= 0.05 ~ "p > 0.05")) %>%
  group_by(Com, direction, Significance, n_ind) %>% 
  summarize(A = n()) %>% 
  ungroup() %>% 
  mutate(A = A/n_ind,
         A = ifelse(direction == "Negative", -A, A),
         Significance = fct_relevel(Significance, "p > 0.05")) %>% 
  ggplot(aes(x = Com, y = A, fill = Significance)) +
  geom_col(color = "black", alpha = 0.8, width = 0.8) +
  geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  coord_flip() +
  labs(x = "Community", y = "Percentage of total coefficients") +
  scale_y_continuous(breaks = seq(-0.5, 1, by = 0.25), limits = c(-0.5, 1),
                     labels = scales::percent) +
  theme(legend.text = element_text(size = 8),
        legend.title = element_text(size = 8))
```

Lobster catches and income showed a increase after the implementation of the reserves for Isla Natividad and Maria Elena, but not for Punta Herrero (Fig \ref{fig:lobsters}). However, the differences in catches and and revenue were not different in the periods before and after the implementation ($p > 0.05$) except for revenues in Isla Natividad, which presented a significant increase of 14.37 (M MXP; $p<0.05$). Table \ref{table:soc_res} presents all the regression coefficients.

```{r, results = "asis"}
C_IN <- filter(L_conapesca, Comunidad == "Isla Natividad") %>% 
  lm(PesoVivo/1000~Post, data = .)

C_ME <- filter(L_conapesca, Comunidad == "Maria Elena") %>% 
  lm(PesoVivo/1000~Post, data = .)

C_PH <- filter(L_conapesca, Comunidad == "Punta Herrero") %>% 
  lm(PesoVivo/1000~Post, data = .)

V_IN <- filter(L_conapesca, Comunidad == "Isla Natividad") %>% 
  lm(Valor/1000000~Post, data = .)

V_ME <- filter(L_conapesca, Comunidad == "Maria Elena") %>% 
  lm(Valor/1000000~Post, data = .)

V_PH <- filter(L_conapesca, Comunidad == "Punta Herrero") %>% 
  lm(Valor/1000000~Post, data = .)

stargazer::stargazer(C_IN, C_ME, C_PH, V_IN, V_ME, V_PH, digits = 2, type = "latex", header = F, omit.stat = c("adj.rsq", "ser", "f"), title = "\\label{table:soc_res} Regression coefficients for lobster catches and revenues for Isla Natividad (1, 4), Maria Elena (2, 5), and Punta Herrero (3, 6).", single.row = T, report = c("vc*"), dep.var.labels = c("Catches (tones)", "Revenue(M MXP)"))

@@

```{r, fig.width = 3.5, fig.height = 4, fig.cap = "\\label{fig:lobsters}Time series of lobster catches (A) and revenues (B) in at Isla Natividad (IN; red circles), Maria Elena (ME; blue triangles), and Punta Herrero (PH; green squares)."}

L_catches <- ggplot(L_conapesca, aes(x = Ano, y = PesoVivo/1000, color = Comunidad, group = Comunidad, fill = Comunidad)) +
  geom_smooth(method = "lm") +
  geom_point(aes(shape = Comunidad), size = 2, alpha = 0.5) +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  geom_vline(xintercept = c(2006, 2012, 2013), color = c("red", "blue", "darkgreen"), linetype = "dashed", size = 0.5) +
  labs(x = "Year", y = "Catches (Tones)") +
  theme(legend.position = "none",
        text = element_text(size = 12))

@@

## Summary of main findings

Our results indicated idiosyncratic biological effects of the reserves across communities and indicators, with a combination of positive and negative effects. However, many of these effects were not statistically significant, indicating no effect of the reserve \ref{fig:res_com}. The socioeconomic indicators pertaining to landings and revenues associated to those landings showed little or no temporal change before and after reserve implementation. These contrasting effects, however, might be clarified when understanding the social-ecological context in which these communities and their reserves sit. In this section, we discuss potential shortcomings in our analysis, and provide plausible explanations to the observed biological and socioeconomic basing on previous literature and our analysis of the social-ecological system.

@@

@@

## Limitations

## Conclusions

# Thoughts from GainesLab Meeting

## General thoughts

A nice story to tell is that reserves need to have optimal social and environmental conditions to work. But they also need to be opttimally designed, accounting for size and location. It is worth mentioning that even when these reserves did not have nice effects on the ecological or fisheries side, they were a project that brought together the community, and also gave fishers access to a network of resources facilitated by the NGO. I still need to get data that support these.

Creo que hay que agregar informacion de la variabilidad ambienta. Posiblemente SST o algo similar. Ver si se puede obtener datos de oxigeno disuelto... Tal vez algo de ENSO / ONI / NAO o algo asi

Quitar analisis de riqueza (la metodologia es restrictiva) y diversidad (aunque shannon provee une buena mezcla del cambio en abundancias y el cambio en riquezas)

revisar biomasa!

Revisar poisson o binomial negativa

Mapa de El Manchon

Las graficas y el analisis de Profit y Catches tienen que ser de langosta entera fresca solamente, y revisar que no haya habido un cambio de commodity a traves del tiempo para justificar usar solamente entera fresca... Tratar de obtener valores hasta 2017

Pedir datos biologicos hasta 2017

Distinguis profit / revenue / income

## Comentarios del Lab

Owen

Are there confounding effects because reserves are so close to control sites?

Dan

Are the data good enough to answer these questions?

Karly

Think about other social indicators that do not depend on catches or revenue from these

Alexa

Daniel

Sebas

Look at other indicators of success (adaptive capacity) in the social / governance data

Steve

Would we expect to see effects in the first five years? (ME and PH)

Are the designs good enough to see effects?

Becky

Ignacia

Perhaps interesting follow-up projects include comparing perceptions vs. reality

Estimating the benefits of being friends with an NGO

@@

```{r}
invert %>%
  filter(generoespecie == "Panulirus interruptus",
         abundancia < 100) %>% 
  abundance(com = "Isla Natividad") %>%
  mutate(ano = as.numeric(ano)) %>%
  ggplot(aes(x = ano, y = indicador, color = zona)) +
  geom_jitter(height = 0, alpha = 0.5) +
  stat_summary(geom = "line", fun.y = mean) +
  scale_color_brewer(palette = "Set1")
```

@@

>>>>

```{r load_data}
invert <- read.csv(file = here::here("data", "invertebrates.csv"),
                stringsAsFactors = T)

fish <- read.csv(file = here::here("data", "fish.csv"),
                stringsAsFactors = T)

conapesca <- read.csv(file = here::here("data", "conapesca.csv"),
                stringsAsFactors = T)

@@

@@

## Abundance commercially important

# Fish
## Biomass
B_IN <- fish %>% 
  biomass(com = "Isla Natividad") %>% 
  model(sfe = F)

@@

Lobster landings and revenue showed a increase after the implementation of the reserves for Isla Natividad and Maria Elena (Fig \ref{fig:lobsters}). However, the differences in catches and and revenue were not different in the periods before and after the implementation ($p > 0.05$) except for revenues in Isla Natividad, which presented a significant increase of 14.37 (M MXP; $p<0.05$). All regression coefficients are presented in **S4 Table**.

@@

# Invert plots
## Lobsters
L_plot <- plot_model(model = list(L_IN, L_ME, L_PH),
                     model_names = c("IS", "ME", "PH"))

## Abundance
I_N <- plot_model(model = list(Ni_IN, Ni_ME, Ni_PH),
                  model_names = c("IN", "ME", "PH"))

# Fish plots
## Biomass
F_B <- plot_model(model = list(B_IN, B_ME, B_PH),
                 model_names = c("IS", "ME", "PH"))

## Abundance
F_N <- plot_model(model = list(N_IN, N_ME, N_PH),
                  model_names = c("IN", "ME", "PH")) +
  theme(legend.justification = c(1, 0),
        legend.position = c(1, 0.55),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        legend.direction = "horizontal")

@@

```{r, fig.height = 3, fig.width = 6, fig.cap = "\\label{fig:res_com}Summarized effects of the marne reserves by direction (positive - negative) and significance."}

observe <- function(model){
  model %>% 
    robust_se() %>%
    filter(grepl("zonaReserva:", term)) %>% 
    mutate(Ano = as.numeric(gsub(term, pattern = "zonaReserva:year", replacement = "")),
           ptest = ((p.value < 0.05)*-1)+0.05)
}

IN <- list(N_IN, Ni_IN, B_IN, L_IN) %>%
  map_df(observe) %>%
  as.tibble() %>% 
  select(estimate, p.value) %>% 
  mutate(Com = "Isla Natividad",
         n_ind = nrow(.))

@@

rbind(IN, ME, PH) %>% 
  mutate(direction = case_when(estimate < 0 ~ "Negative",
                               estimate > 0 ~ "Positive"),
         Significance = case_when(p.value < 0.05 ~ "p < 0.05",
                            p.value >= 0.05 ~ "p > 0.05")) %>%
  group_by(Com, direction, Significance, n_ind) %>% 
  summarize(A = n()) %>% 
  ungroup() %>% 
  mutate(A = A/n_ind,
         A = ifelse(direction == "Negative", -A, A),
         Significance = fct_relevel(Significance, "p > 0.05")) %>% 
  ggplot(aes(x = Com, y = A, fill = Significance)) +
  geom_col(color = "black", alpha = 0.8, width = 0.8) +
  geom_hline(yintercept = 0, linetype = "dashed", size = 1) +
  scale_fill_brewer(palette = "Set1", direction = -1) +
  coord_flip() +
  labs(x = "Community", y = "Percentage of total coefficients") +
  scale_y_continuous(breaks = seq(-0.5, 1, by = 0.25), limits = c(-0.5, 1),
                     labels = scales::percent) +
  theme(legend.text = element_text(size = 8),
        legend.title = element_text(size = 8),
        text = element_text(size = 12))
```

```{r, results = "asis"}
C_IN <- conapesca %>% 
  filter(years_centered > -10) %>% 
  mutate(years_centered = as.factor(years_centered)) %>% 
  filter(comunidad == "Isla Natividad" | is.na(comunidad)) %>% 
  filter(zona == "PN") %>%
  lm(pesovivo/1e3 ~ grupo * years_centered + unidadeconomica, data = .)

C_ME <- conapesca %>% 
  filter(years_centered > -10) %>% 
  mutate(years_centered = as.factor(years_centered)) %>% 
  filter(comunidad == "Maria Elena" | is.na(comunidad)) %>% 
  filter(zona == "MC") %>%
  lm(pesovivo/1e3 ~ grupo * years_centered + unidadeconomica, data = .)

V_IN <- conapesca %>% 
  filter(years_centered > -10) %>% 
  mutate(years_centered = as.factor(years_centered)) %>% 
  filter(comunidad == "Isla Natividad" | is.na(comunidad)) %>% 
  filter(zona == "PN") %>%
  lm(valor/1e6 ~ grupo * years_centered + unidadeconomica, data = .)

V_ME <- conapesca %>% 
  filter(years_centered > -10) %>% 
  mutate(years_centered = as.factor(years_centered)) %>% 
  filter(comunidad == "Maria Elena" | is.na(comunidad)) %>% 
  filter(zona == "MC") %>%
  lm(valor/1e6 ~ grupo * years_centered + unidadeconomica, data = .)

#soc_res se fue

plot_socioeco <- function(model_list, model_names, ylab){

  extract_filter <- function(model, name){
    model %>% 
      robust_se() %>% 
      filter(grepl(pattern = "grupoTreated:years_centered", x = term)) %>% 
      mutate(years_centered = as.numeric(gsub(pattern = "grupoTreated:years_centered",
                                              replacement = "",
                                              x = term)),
             Community = name)
  }

  purrr::map2_df(model_list, model_names, extract_filter) %>% 
    ggplot(aes(x = years_centered, y = estimate, group = Community)) +
    geom_hline(yintercept = 0,
               linetype = "dashed",
               size = 1) +
    geom_vline(xintercept = 0,
               linetype = "dashed",
               size = 1) +
    geom_errorbar(aes(color = Community,
                      ymin = estimate-std.error,
                      ymax = estimate + std.error),
                  width = 0.1,
                  size = 1,
                  position = position_dodge(width = 0.4)) +
    geom_point(aes(color = Community, shape = Community),
               size = 4,
               position = position_dodge(width = 0.4),
               alpha = 0.5) +
    scale_color_brewer(palette = "Set1") +
    labs(x = "Years since implementation", y = ylab) +
    theme(text = element_text(size = 12))
}
```

```{r, fig.width = 5, fig.height = 4, fig.cap = "\\label{fig:lobsters}Effect sizes for lobster catches (A) and revenues (B) in at Isla Natividad (IN; red circles) and Maria Elena (ME; blue triangles)"}

c_plot <- plot_socioeco(model_list = list(C_IN, C_ME),
                        model_names = list("IN", "ME"),
                        ylab = "Landings (K MT)")

v_plot <- plot_socioeco(model_list = list(V_IN, V_ME),
                        model_names = list("IN", "ME"),
                        ylab = "Revenue (M MXP)")

plot_grid(c_plot, v_plot, ncol = 1)

@@

@@

Our results show idiosyncratic biological effects of the reserves across communities and indicators. However, many of these effects were not statistically significant, indicating no effect of the reserve \ref{fig:res_com}. The socioeconomic indicators pertaining to landings and revenues associated to those landings showed little or no temporal change before and after reserve implementation. These contrasting effects, however, might be clarified when understanding the social-ecological context in which these communities and their reserves sit. In this section, we discuss potential shortcomings in our analysis, and provide plausible explanations to the observed biological and socioeconomic basing on previous literature and our analysis of the social-ecological system.

@@

**Limitations...**

@@

<!-- # Thoughts from GainesLab Meeting -->

<!-- ## General thoughts -->

<!-- A nice story to tell is that reserves need to have optimal social and environmental conditions to work. But they also need to be opttimally designed, accounting for size and location. It is worth mentioning that even when these reserves did not have nice effects on the ecological or fisheries side, they were a project that brought together the community, and also gave fishers access to a network of resources facilitated by the NGO. I still need to get data that support these. -->

<!-- Creo que hay que agregar informacion de la variabilidad ambienta. Posiblemente SST o algo similar. Ver si se puede obtener datos de oxigeno disuelto... Tal vez algo de ENSO / ONI / NAO o algo asi -->

<!-- Quitar analisis de riqueza (la metodologia es restrictiva) y diversidad (aunque shannon provee une buena mezcla del cambio en abundancias y el cambio en riquezas) -->

<!-- revisar biomasa! -->

<!-- Revisar poisson o binomial negativa -->

<!-- Mapa de El Manchon -->

<!-- Las graficas y el analisis de Profit y Catches tienen que ser de langosta entera fresca solamente, y revisar que no haya habido un cambio de commodity a traves del tiempo para justificar usar solamente entera fresca... Tratar de obtener valores hasta 2017 -->

<!-- Pedir datos biologicos hasta 2017 -->

<!-- ## Comentarios del Lab -->

<!-- Owen -->

<!-- Are there confounding effects because reserves are so close to control sites? -->

<!-- Dan -->

<!-- Are the data good enough to answer these questions? -->

<!-- Karly -->

<!-- Think about other social indicators that do not depend on catches or revenue from these -->

<!-- Alexa -->

<!-- Daniel -->

<!-- Sebas -->

<!-- Look at other indicators of success (adaptive capacity) in the social / governance data -->

<!-- Steve -->

<!-- Would we expect to see effects in the first five years? (ME and PH) -->

<!-- Are the designs good enough to see effects? -->

<!-- Becky -->

<!-- Ignacia -->

<!-- Perhaps interesting follow-up projects include comparing perceptions vs. reality -->

<!-- Estimating the benefits of being friends with an NGO -->

@@

```{r, eval = F}
invert %>%
  filter(generoespecie == "Panulirus interruptus",
         abundancia < 100) %>% 
  abundance(com = "Isla Natividad") %>%
  mutate(ano = as.numeric(ano)) %>%
  ggplot(aes(x = ano, y = indicador, color = zona)) +
  geom_jitter(height = 0, alpha = 0.5) +
  stat_summary(geom = "line", fun.y = mean) +
  scale_color_brewer(palette = "Set1")
```

@@

```{r, eval = F}

# Series de tiempo de langosta
L_catches <- ggplot(L_conapesca,
                    aes(x = Ano,
                        y = PesoVivo/1000,
                        color = Comunidad,
                        group = Comunidad,
                        fill = Comunidad)) +
  geom_smooth(method = "lm") +
  geom_point(aes(shape = Comunidad), size = 2, alpha = 0.5) +
  scale_color_brewer(palette = "Set1") +
  scale_fill_brewer(palette = "Set1") +
  geom_vline(xintercept = c(2006, 2012, 2013),
             color = c("red", "blue", "darkgreen"),
             linetype = "dashed", size = 0.5) +
  labs(x = "Year", y = "Catches (Tones)") +
  theme(legend.position = "none",
        text = element_text(size = 12))

### 2018-04-10 docs/paper/Villasenor-Derbez.tex
fixed mistakes due to reorganization of repo
Added render date to PDF
Updated manuscript with new model and included CI for socioeco graphs

@@

\caption{\label{tab:unnamed-chunk-2}\label{table:com_sum} Summary of commuity--based marine reserves by community. Imp = Year of implementation, Start = Year of first sampling, number of fish transects in control (Cf) and reserve (Rf) sites, and number of invertebrate transects in Control (Ci) and Reserve (Ri) sites.}
\centering
\begin{tabular}[t]{l|l|r|r|r|r|r|r}
\hline
Community & Reserve - Control & Imp & Start & Cf & Rf & Ci & Ri\\
\hline
Isla Natividad & La Plana / Las Cuevas - La Dulce / Babencho & 2006 & 2006 & 405 & 242 & 415 & 245\\
\hline
Maria Elena & Cabezo - Cabezo (Control) & 2012 & 2012 & 44 & 45 & 27 & 21\\
\hline
Punta Herrero & El Faro - El Faro (Control) & 2013 & 2013 & 39 & 40 & 24 & 32\\
\hline
Punta Herrero & Manchon - Manchon (Control) & 2013 & 2012 & 43 & 45 & 27 & 42\\
\hline
\end{tabular}
\end{table}

@@

@@

Lobster catches and income showed a increase after the implementation of
the reserves for Isla Natividad and Maria Elena, but not for Punta
Herrero (Fig \ref{fig:lobsters}). However, the differences in catches
and and revenue were not different in the periods before and after the
implementation (\(p > 0.05\)) except for revenues in Isla Natividad,
which presented a significant increase of 14.37 (M MXP; \(p<0.05\)).
Table \ref{table:soc_res} presents all the regression coefficients.

\begin{table}[!htbp] \centering 
  \caption{\label{table:soc_res} Regression coefficients for lobster catches and revenues for Isla Natividad (1, 4), Maria Elena (2, 5), and Punta Herrero (3, 6).} 
  \label{} 
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{\textit{Dependent variable:}} \\ 
\cline{2-7} 
\\[-1.8ex] & \multicolumn{3}{c}{Catches (tones)} & \multicolumn{3}{c}{Revenue(M MXP)} \\ 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\ 
\hline \\[-1.8ex] 
 Post & 7.37 & 5.83 & $-$1.26 & 14.37$^{***}$ & 1.24 & $-$0.06 \\ 
  Constant & 122.68$^{***}$ & 11.41$^{***}$ & 6.06$^{***}$ & 10.89$^{***}$ & 2.04$^{***}$ & 1.06$^{***}$ \\ 
 \hline \\[-1.8ex] 
Observations & 15 & 14 & 13 & 15 & 14 & 13 \\ 
R$^{2}$ & 0.02 & 0.04 & 0.01 & 0.52 & 0.04 & 0.0004 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{6}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
\end{tabular} 
\end{table}

\begin{figure}
\centering
\includegraphics{Villasenor-Derbez_files/figure-latex/unnamed-chunk-8-1.pdf}
\caption{\label{fig:unnamed-chunk-8}\label{fig:lobsters}Time series of
lobster catches (A) and revenues (B) in at Isla Natividad (IN; red
circles), Maria Elena (ME; blue triangles), and Punta Herrero (PH; green
squares).}
\end{figure}

@@

Our results indicated idiosyncratic biological effects of the reserves
across communities and indicators, with a combination of positive and
negative effects. However, many of these effects were not statistically
significant, indicating no effect of the reserve \ref{fig:res_com}. The
socioeconomic indicators pertaining to landings and revenues associated
to those landings showed little or no temporal change before and after
reserve implementation. These contrasting effects, however, might be
clarified when understanding the social-ecological context in which
these communities and their reserves sit. In this section, we discuss
potential shortcomings in our analysis, and provide plausible
explanations to the observed biological and socioeconomic basing on
previous literature and our analysis of the social-ecological system.

@@

>>>>

\textbf{Last\_update}: 2018-04-10

@@

\caption{\label{tab:unnamed-chunk-2}\label{table:com_sum} Summary of commuity--based marine reserves by community. Imp = Year of implementation, Start = Year of first sampling, number of fish transects in control (Cf) and reserve (Rf) sites, and number of invertebrate transects in Control (Ci) and Reserve (Ri) sites.}
\centering
\begin{tabular}[t]{l|l|r|r|r|r|r|r}
\hline
Community & Reserve - Control & Imp & Start & Cf & Rf & Ci & Ri\\
\hline
Isla Natividad & La Plana / Las Cuevas - La Dulce / Babencho & 2006 & 2006 & 400 & 241 & 415 & 244\\
\hline
Maria Elena & Cabezo - Cabezo (Control) & 2012 & 2012 & 44 & 45 & 27 & 21\\
\hline
Punta Herrero & El Faro - El Faro (Control) & 2013 & 2013 & 39 & 40 & 24 & 32\\
\hline
Punta Herrero & Manchon - Manchon (Control) & 2013 & 2012 & 43 & 45 & 27 & 41\\
\hline
\end{tabular}
\end{table}

@@

Lobster landings and revenue showed a increase after the implementation
of the reserves for Isla Natividad and Maria Elena (Fig
\ref{fig:lobsters}). However, the differences in catches and and revenue
were not different in the periods before and after the implementation
(\(p > 0.05\)) except for revenues in Isla Natividad, which presented a
significant increase of 14.37 (M MXP; \(p<0.05\)). All regression
coefficients are presented in \textbf{S4 Table}.

@@

\begin{figure}
\centering
\includegraphics{Villasenor-Derbez_files/figure-latex/unnamed-chunk-8-1.pdf}
\caption{\label{fig:unnamed-chunk-8}\label{fig:lobsters}Effect sizes for
lobster catches (A) and revenues (B) in at Isla Natividad (IN; red
circles) and Maria Elena (ME; blue triangles)}
\end{figure}

@@

Our results show idiosyncratic biological effects of the reserves across
communities and indicators. However, many of these effects were not
statistically significant, indicating no effect of the reserve
\ref{fig:res_com}. The socioeconomic indicators pertaining to landings
and revenues associated to those landings showed little or no temporal
change before and after reserve implementation. These contrasting
effects, however, might be clarified when understanding the
social-ecological context in which these communities and their reserves
sit. In this section, we discuss potential shortcomings in our analysis,
and provide plausible explanations to the observed biological and
socioeconomic basing on previous literature and our analysis of the
social-ecological system.

@@

\textbf{Limitations\ldots{}}
